%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Colten}{Cross}{ \urlstyle{same}\url{www.cwcross.com} \\
\href{mailto:colten@cwcross.com}{colten@cwcross.com} | (762) 207-0132}

\vspace{5mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     SUMMARY
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{SUMMARY}
\begin{flushleft}
Web Developer with strong skills in Front End languages such as JavaScript, HTML5/CSS3, and Javascript frameworks including jQuery and Google Polymer. Independently learning Back End languages and frameworks PHP and Symfony through personal projects. 
\end{flushleft}

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Georgia State University}
\location{May 2017 | Atlanta, GA}
\descript{BS in Physics}
\descript{Comp Sci concentration}
\location{ Cum. GPA: 3.47 / 4.0 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/ColCross}{\custombold{ColCross}} \\
LinkedIn://  \href{https://www.linkedin.com/in/coltencross}{\custombold{ColtenCross}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}
\descript{CompTIA Security+}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Clearance
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Security Clearance}
\descript{DoD Secret}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\custombold{Software Engineering} \\
\custombold{Web Development} \\
\custombold{Data Structures} \\
\custombold{System-Level Programming} \\
\custombold{Math Models of Comp Sci} \\
Linear Algebra \\
Robotics Engineering 1 \\
Electronics \\
Modern Physics \\
Statistical and Thermal Physics \\
Calculus I, II, III \\
Differential Equations \\
Classical Mechanics \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 
2016 - Sigma Pi Sigma (Physics Honor Society)\\
2014 - National Society of Collegiate Scholars\\
2012 - National Honor Society\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\descript{Programming Languages / Frameworks}
JavaScript \textbullet{} HTML/CSS \textbullet{} Git \textbullet{} jQuery \textbullet{} Java \textbullet{} Polymer \textbullet{} SQL \textbullet{} Bootstrap\\
\descript{Software}
VSC \textbullet{} IntelliJ \textbullet{} Eclipse \textbullet{} WebStorm \textbullet{} VirtualBox \textbullet{} AutoCAD \textbullet{} MS Office \\
\descript{Operating Systems}
OS X \textbullet{} Windows \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{Cartoon Network - Turner}
\descript{| Web Developer Intern}
\location{Aug 2017 – Present | Atlanta, GA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Utilizing JavaScript and jQuery to convert Cartoon Network website login and registration functionality to a new internal system and API.
\item Collaborating with designers to implement new front-end redesign for registration and login using HTML5/CSS3.
\item Using Git to maintain source control and merge code into staging and production environments.
\item Employing full Agile methodologies through daily scrums and the JIRA ticketing system.
\item Interacting with Cartoon Network Amazon S3 buckets to retrieve and store relevant files.
\item Working with third party companies such as Lego and Hasbro through promotional game marketing.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Dog's out of the Bag}
\descript{| \urlstyle{same}\url{https://git.io/vF3WX}}
\location{Oct 2017 – Present | Atlanta, GA}
A small, unfinished blog template I am building in order to learn PHP and Symfony which power the Drupal framework being implemented by Cartoon Network. The site pulls and stores blog posts from a MySQL database, and currently allows editing and deleting posts.
\sectionsep

\runsubsection{Muon Telescope}
\descript{| \urlstyle{same}\url{https://git.io/vF3ce}}
\location{Jan 2017 – April 2017 | Atlanta, GA}
Assisted in designing and implementing a modular website for displaying data from Georgia State University's cosmic ray detector network. Utilized Polymer to implement front-end web design, and a RESTful API amd MySQL for back-end database querying and management.
\sectionsep

\runsubsection{Project Overdrive}
\descript{| \urlstyle{same}\url{https://git.io/vF3cL}}
\location{Jan 2017 – April 2017 | Atlanta, GA}
Worked as a team through every stage of the software development process including design, documentation, and implementation. Utilized Java and SQLite to implement design requirements.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Additional Work Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\descript{Additional Work Experience}
\begin{tightemize}
\item Geek Squad (Best Buy) - Advanced Repair Agent (Sep 2017 - Present)
\item GSU - Teaching and Learning Assistant (Sep 2016 - May 2017)
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}